Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-19 Thesis/chapter/062-post-emma.tex
start Grid Seach

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
For \gls{krr} and {svm} I had to find out what the ideal hyper parameters were. 
So, I anstellen a grid search with the following hyperparameters: 
%kernel=["poly","rbf"]#,"sigmoid"]
%C= np.array(range(1,20))*0.05
%degree=range(1,6)
%epsilon= np.array(range(1,20))*0.2
%gamma=[0.0,0.1,1.0,10.0]
%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
Now what are C,epsilon and gamma?

@@

\begin{table}[htb]
	\centering
    \caption{Post EMMA vergleich}
	\label{tab:post-emma}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    G&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
        ML KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        ML SVM& 15  415&    26& 1050&   28& 1588&   19& 677\\
    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    p&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
        ML KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        ML SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
    \hline\hline
	\end{tabular}
\end{table}

>>>>

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
For \gls{krr} and {svm} I had to find out what the ideal hyper parameters were. 
So, I anstellen a grid search with the following hyperparameters: 
%kernel=["poly","rbf"]#,"sigmoid"]
%C= np.array(range(1,20))*0.05
%degree=range(1,6)
%epsilon= np.array(range(1,20))*0.2
%gamma=[0.0,0.1,1.0,10.0]
%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
Now what are C,epsilon and gamma?

\td{which parameters}
The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
The kernels for \gls{svm} were the same and further hyper parameters were 
$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--1 with 0.05 steps, $\varepsilon$ 0.02--4 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
\td{how, every combination}
Each grid search calculation was calculated with and without scaling the data before the optimisation. 
For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated.

\td{what were best results/hyper parameters}

%# KRR
%# some kind of scaling factor; can be set to auto/scale, include into list? 
%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
%# alpha: bigger alpha, bigger regularisation 
%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS

% SVM
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
%# regularization parameter
%C= np.array(range(1,20))*0.05 # HPGS
%# epsilon-tube size for no penalty; rather large 
%epsilon= np.array(range(1,20))*0.2 # HPGS
%# some kind of scaling factor; can be set to auto/scale, include into list?  
%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS

@@

\begin{table}[htb]
	\centering
    \caption{Post EMMA vergleich}
	\label{tab:post-emma}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    G&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        SVM& 15  415&    26& 1050&   28& 1588&   19& 677\\
    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    p&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
    \hline\hline
	\end{tabular}
\end{table}
